Generate Networks

### 2015-09-08 code/01_generate_networks.Rmd
modify code to comply better with igraph 1.0
update script to match new data structure

```{r}
data <- read.csv("./data/network_data/Bartomeus_Ntw_nceas.txt",sep="\t") %>%
	tbl_df() %T>% print(width = Inf)

@@

	net <- igraph::graph.data.frame(edg, directed = F, vertices = ver)
	list(net = net,
			 match = igraph::maximum.bipartite.matching(net))
})
```

>>>>

```{r}
data <- read.csv("./data/bartomeus/Bartomeus_Ntw_nceas.txt",sep="\t") %>%
	tbl_df() %T>% print(width = Inf)

@@

	net <- igraph::graph_from_data_frame(edg, directed = F, vertices = ver)
	list(net = net,
			 match = igraph::maximum.bipartite.matching(net))
})
```
